\section{Experience}
	\cventry{March 2023 --\\Present}
		{Ontra Mobility}
		{CTO}
		{New York, New York}{}
		{Building a next generation platform for planning and operating on-demand multimodal transit systems.}
	\cventry{Nov 2023 --\\Present}
		{AI Institute for Advances in Optimization}
		{Research Engineer}
		{New York, New York}{}
		{Leading a team of Ph.D. students and Postdocs to build a SaaS platform for operating on-demand multimodal tranist systems. \\
		Developing state-of-the-art algorithms for trip-planning and ridesharing with transfers to fixed-route. \\
		Interfacing with our partners at Chatham Area Transit to deploy our software in Savannah, GA.}
	\cventry{Aug 2022 --\\Nov 2023}
		{Google}
		{Software Engineer}
		{New York, New York}{}
		{Developing, testing, and deploying new features for Google Display Ads to optimize revenue.}
	\cventry{Sept 2018 --\\Aug 2022}
		{Georgia Institute of Technology}
		{Research Assistant}
		{Atlanta, Georgia}{}
		{Designing and deploying microservices on Azure Kubernetes Service for \href{https://www.itsmarta.com/reach.aspx}{MARTA Reach, an on-demand ride-sharing service in Atlanta, GA}. \\
        Developing state-of-the-art optimization and artificial intelligence software using C\texttt{++} for operating on-demand ride-sharing and multimodal transit systems. \\
        Created and maintained a python library using boost to wrap high-performance C\texttt{++} code for use by less technical users.}
	\cventry{May 2016 --\\Aug 2018}
		{The University of Michigan}
		{Research Assistant}
		{Ann Arbor, Michigan}{}
		{Developing simulation, optimization, and artificial intelligence software in C\texttt{++} and python for the design and operation of multimodal transit systems. \\
		Deployed an \href{https://record.umich.edu/articles/north-campus-first-test-site-hybrid-transportation-system/}{on-demand ride-sharing service at U-M} using redis queues for pub/sub with websockets, rabbitmq and celery for managing distributed task queues, and mongoDB for storing state information.}
	\cventry{Dec 2014 --\\May 2016}
		{Center for Voting Technology Research}
		{Undergraduate Research Assistant}
		{Storrs, Connecticut}{}
        {Wrote python scripts to evalutate the functionality and security of various electronic pollbook solutions.}

	\cventry{May 2015 --\\Aug 2015}
		{United Technologies Building \& Industrial Systems (UTC) -- Otis Elevator Company}
		{Engineering Intern}
		{Farmington, Connecticut}{}
		{Developed a Java application to translate UI labels, stored in XML, into the spoken language selected by the user.}

	\cventry{Aug 2014 --\\Dec 2014}
		{Cigna Corporation}
		{Software Development Intern}
		{Storrs, Connecticut}{}
        {}
	\cventry{June 2014 --\\Aug 2014}
		{Travelers Insurance Company}
		{IT Intern}
		{Hartford, Connecticut}{}
        {}
